ABM simulating short-term mating behaviors

### 2022-06-01 submission/manuscript.Rmd
added plots for in-pool difference

Yurun Ying^1^, Jan Antfolk^2^, Pekka Santtila^1^^,^^3^^,^^$\dagger$^

@@

^$\dagger$^ To whom correspondence should be addressed: [pekka.santtila@nyu.edu](pekka.santtila@nyu.edu)

@@

In Experiment 1, there was a smaller proportion of heterosexual men in the mating pool (*M* = `r m_inpool.mean_011/N`, *SD* = `r m_inpool.sd_011/N`) compared to women (*M* = `r f_inpool.mean_011/N`, *SD* = `r f_inpool.sd_011/N`)), *t*(`r inpool.parameter_011`) = `r inpool.statistic_011`, *p* `r inpool.p.value_011`, Cohen's *d* = `r inpool.d_011`. In this population, there were gender differences in short-term mating behaviors when men and women had differential preferences for short-term mating (Figure **x**). The average number of short-term mating experiences was higher among heterosexual men (*M* = `r m_exp_ip.mean_011`, *SD* = `r m_exp_ip.sd_011`) than among heterosexual women (*M* = `r f_exp_ip.mean_011`, *SD* = `r f_exp_ip.sd_011`), *t*(`r exp_ip.parameter_011`) = `r exp_ip.statistic_011`, *p* `r exp_ip.p.value_011`, Cohen's *d* = `r exp_ip.d_011`. Likewise, the average number of short-term mates was higher among heterosexual men (*M* = `r m_partner_ip.mean_011`, *SD* = `r m_partner_ip.sd_011`) than among heterosexual women (*M* = `r f_partner_ip.mean_011`, *SD* = `r f_partner_ip.sd_011`), *t*(`r partner_ip.parameter_011`) = `r partner_ip.statistic_011`, *p* `r partner_ip.p.value_011`, Cohen's *d* = `r partner_ip.d_011`.

>>>>

Yurun Ying^1^^,^^$\dagger$^, Jan Antfolk^2^, Pekka Santtila^1^^,^^3^

@@

^$\dagger$^ To whom correspondence should be addressed: [yurun.ying@nyu.edu](yurun.ying@nyu.edu)

@@

In Experiment 1, there was a smaller proportion of heterosexual men in the mating pool (*M* = `r m_inpool.mean_011/N`, *SD* = `r m_inpool.sd_011/N`) compared to women (*M* = `r f_inpool.mean_011/N`, *SD* = `r f_inpool.sd_011/N`), *t*(`r inpool.parameter_011`) = `r inpool.statistic_011`, *p* `r inpool.p.value_011`, Cohen's *d* = `r inpool.d_011`. In this population, there were gender differences in short-term mating behaviors when men and women had differential preferences for short-term mating (Figure \ref{fig:men_vs_women_inpool}). The average number of short-term mating experiences was higher among heterosexual men (*M* = `r m_exp_ip.mean_011`, *SD* = `r m_exp_ip.sd_011`) than among heterosexual women (*M* = `r f_exp_ip.mean_011`, *SD* = `r f_exp_ip.sd_011`), *t*(`r exp_ip.parameter_011`) = `r exp_ip.statistic_011`, *p* `r exp_ip.p.value_011`, Cohen's *d* = `r exp_ip.d_011`. Likewise, the average number of short-term mates was higher among heterosexual men (*M* = `r m_partner_ip.mean_011`, *SD* = `r m_partner_ip.sd_011`) than among heterosexual women (*M* = `r f_partner_ip.mean_011`, *SD* = `r f_partner_ip.sd_011`), *t*(`r partner_ip.parameter_011`) = `r partner_ip.statistic_011`, *p* `r partner_ip.p.value_011`, Cohen's *d* = `r partner_ip.d_011`.

\begin{figure}[h]
  \centering
  \includegraphics[width=0.8\columnwidth]{figures/fig2_men_vs_women_inpool.pdf}
  \caption{\textbf{Short-term mating behaviors of heterosexual men and women in the mating pool after 1,000 time steps in the model when gender differences existed in mating preferences.} Violin plots summarizing the outcome variables. Plot (A) shows the average number of short-term mating experiences in the mating pool, and plot (B) shows the average number of short-term mates in the mating pool. Central points show mean values and whiskers represent standard errors, but the standard errors are small and overlap to form a single bar. The averages were calculated using the population of heterosexual men and women in the mating pool (\textit{M\textsubscript{men}} = `r m_inpool.mean_011`, \textit{M\textsubscript{men}} = `r f_inpool.mean_011`).}
  \label{fig:men_vs_women_inpool}
\end{figure}

### 2022-06-01 submission/manuscript.tex
added plots for in-pool difference

Yurun Ying\textsuperscript{1}, Jan Antfolk\textsuperscript{2}, Pekka
Santtila\textsuperscript{1,3,\(\dagger\)}

@@

\textsuperscript{\(\dagger\)} To whom correspondence should be
addressed: \url{pekka.santtila@nyu.edu}

@@

In Experiment 1, there was a smaller proportion of heterosexual men in
the mating pool (\emph{M} = 0.38, \emph{SD} = 0.04) compared to women
(\emph{M} = 0.51, \emph{SD} = 0.05)), \emph{t}(4,998) = 104.85, \emph{p}
\textless{} .001, Cohen's \emph{d} = 2.97. In this population, there
were gender differences in short-term mating behaviors when men and
women had differential preferences for short-term mating (Figure
\textbf{x}). The average number of short-term mating experiences was
higher among heterosexual men (\emph{M} = 3.78, \emph{SD} = 0.50) than
among heterosexual women (\emph{M} = 2.79, \emph{SD} = 0.35),
\emph{t}(4,998) = -81.53, \emph{p} \textless{} .001, Cohen's \emph{d} =
2.31. Likewise, the average number of short-term mates was higher among
heterosexual men (\emph{M} = 2.12, \emph{SD} = 0.17) than among
heterosexual women (\emph{M} = 1.56, \emph{SD} = 0.11), \emph{t}(4,998)
= -135.85, \emph{p} \textless{} .001, Cohen's \emph{d} = 3.84.

>>>>

Yurun Ying\textsuperscript{1,\(\dagger\)}, Jan
Antfolk\textsuperscript{2}, Pekka Santtila\textsuperscript{1,3}

@@

\textsuperscript{\(\dagger\)} To whom correspondence should be
addressed: \url{yurun.ying@nyu.edu}

@@

In Experiment 1, there was a smaller proportion of heterosexual men in
the mating pool (\emph{M} = 0.38, \emph{SD} = 0.04) compared to women
(\emph{M} = 0.51, \emph{SD} = 0.05), \emph{t}(4,998) = 104.85, \emph{p}
\textless{} .001, Cohen's \emph{d} = 2.97. In this population, there
were gender differences in short-term mating behaviors when men and
women had differential preferences for short-term mating (Figure
\ref{fig:men_vs_women_inpool}). The average number of short-term mating
experiences was higher among heterosexual men (\emph{M} = 3.78,
\emph{SD} = 0.50) than among heterosexual women (\emph{M} = 2.79,
\emph{SD} = 0.35), \emph{t}(4,998) = -81.53, \emph{p} \textless{} .001,
Cohen's \emph{d} = 2.31. Likewise, the average number of short-term
mates was higher among heterosexual men (\emph{M} = 2.12, \emph{SD} =
0.17) than among heterosexual women (\emph{M} = 1.56, \emph{SD} = 0.11),
\emph{t}(4,998) = -135.85, \emph{p} \textless{} .001, Cohen's \emph{d} =
3.84.

\begin{figure}[h]
  \centering
  \includegraphics[width=0.8\columnwidth]{figures/fig2_men_vs_women_inpool.pdf}
  \caption{\textbf{Short-term mating behaviors of heterosexual men and women in the mating pool after 1,000 time steps in the model when gender differences existed in mating preferences.} Violin plots summarizing the outcome variables. Plot (A) shows the average number of short-term mating experiences in the mating pool, and plot (B) shows the average number of short-term mates in the mating pool. Central points show mean values and whiskers represent standard errors, but the standard errors are small and overlap to form a single bar. The averages were calculated using the population of heterosexual men and women in the mating pool (\textit{M\textsubscript{men}} = 56.85, \textit{M\textsubscript{men}} = 77.04).}
  \label{fig:men_vs_women_inpool}
\end{figure}
